
## (a)

#https://www.rstudio.com/conference/2022/talks/achieving-seamless-workflow-r-python/

Brief Summary

Statistics Canada is the official statistical agency of Canada, and it is a large institution with over 6,000 employees. It has a legal obligation to ensure the privacy of personal information, which is why it has implemented an internal system called G-Confid to prevent the disclosure of confidential information, and this system is exclusively implemented using the SAS programming language. As a result, many analysts and data scientists at Statistics Canada are required to use the SAS programming language as part of their workflow. Therefore, finding ways to seamlessly work between open-source programming languages and SAS is of utmost importance.
Melissa offers a solution to create a harmonious workflow for R, Python, and SAS within RStudio. This approach provides a recipe that will help both data scientists and analysts effectively perform their tasks.

## (b)

# Differences between R and Python (R and Python respectively)

#When defining a variable

```{r}
X <- 5
```
```{Python}
X = 5
```
#When creating a list

```{r}
numbers <- c(1, 2, 3)
```
```{Python}
numbers = [1, 2, 3]
```
#When performing arithmetic operations

```{r}
result <- 2 + 3 * 5 
```
```{Python}
result = 2 + 3 * 5
```






